Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-12 manuscript/manuscript.tex
adds updated climate sensitivity figure for all vital rate combos

Our goal was not make any explicit forecast for the future state of
these populations based on predicted climate change. But our results
highlight the state of affairs in ecology when it comes to forecasting
the impacts of climate change. The analysis we conducted here could be
considered, with some exceptions of course, at the forefront of
ecological forecasting in terms of the statistical approach employed
(hierarchical Bayesian), the type of population model we used
(stochastic IPM with parameter uncertainty), and the amount of data we
had at our disposal (14 years of individual-level data).

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Proportional change in species' mean cover caused by a 1\%
increase in observed precipitation, temperature, or both as predicted by
the individual-based IPM and the aggregate-based QBM. Note that the
change for POSE due to a precipitation increase predicted by the QBM is
almost zero and so does not show up in the figure. Labels on x-axis
refer to: `ppt' = 1\% increase in mean precipitation; `temp' = 1\%
increase in mean temperature; `ppt + temp' = 1\% increase in mean
precipitation and mean temperature.}
\end{figure}

>>>>

Our goal was not make any explicit forecast for the future state of
these populations based on predicted climate change. But our results
highlight the state of affairs in ecology when it comes to forecasting
the impacts of climate change. The analysis we conducted here could be
considered, with some exceptions of course, at the forefront of
ecological forecasting in terms of the statistical approach employed
(hierarchical Bayesian), the type of population model we used
(stochastic IPM with parameter uncertainty), and the amount of data we
had at our disposal (14 years of individual-level data). Yet, model
predictions proved so uncertain that any forecast, when bounded with
uncertainty, would be at best not useful and at worst meaningless.

Something about fitting the models\ldots{}then cite Britta's paper:
20-25 years needed!

@@
